A biometric analysis of infant mortality and temperature, northern Sweden 1895-1950

### 2022-01-15 paper.Rmd
fixes
spell check

One important reason for studying neonatal and postneonatal mortality separately is the 
findings by Bourgeouis-Pichat [@bp51a;  @bp51b] about endogeneous and exogeneous mortality and the log-cube transform,
so we start by recollecting his results and formulate them in a modern statistical setting.

# The Bourgeouis-Pichat model

Bourgeouis-Picat (*B-P*) suggests that mortality
during the last eleven months (28 days) of infancy follows a *uniform* distribution
given a specific transformation of time (age), the 
*log-cube transformation* $g$.

@@

# Infant mortality, climate, and weather

The analyses are performed on the log-cube scale with proportional hazards modelling. Note that
the property of proportional hazards are preserved under a strictly monotone increasing time transform.
However, the estimates of baseline distribution characteristics will change.

>>>>

One important reason for studying neonatal and postneonatal mortality separately is the 
findings by Bourgeois-Pichat [@bp51a;  @bp51b] about endogenous and exogenous mortality and the log-cube transform,
so we start by recollecting his results and formulate them in a modern statistical setting.

# The Bourgeois-Pichat model

Bourgeois-Pichat (*B-P*) suggests that mortality
during the last eleven months (28 days) of infancy follows a *uniform* distribution
given a specific transformation of time (age), the 
*log-cube transformation* $g$.

@@

# Infant mortality, climate and weather

The analyses are performed on the log-cube scale with proportional hazards modelling. Note that
the property of proportional hazards are preserved under a strictly monotone increasing time transform.
However, the estimates of baseline distribution characteristics will change, of course.
